---
title: "Create Final Data Set Indirect Effects Aim 1"
author: "Ryan Malosh"
date: "June 6, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

setwd("C:/Users/rmalosh/Box Sync/Indirect Effects R03/Aim 1")
data <- readRDS("Data/AnalysisData.RDS")      
      
```
Objective: To estimate the indirect effect of influenza vaccine over 8 seasons

Analysis database will contain the variables as described in "C:/Users/rmalosh/Box Sync/Indirect Effects R03/Aim 1/Data/Aim 1 Data Dictionary.xlsx"

## Methods

We used longitudinal data from the Household Influenza Vaccine Evaluation (HIVE) study collected from 2010-2011 through 2017-2018 influenza seasons.  

First we will make sure seasonal databases have expected number of individuals and households
```{r }
setwd("C:/Users/rmalosh/Box Sync/Indirect Effects R03/Aim 1/")

ggsave("R Output/Flu count by season.png", width = 9, height = 6, units="in")
ggplot(data, aes(flu.count)) +
  geom_histogram(binwidth = 1) + 
  facet_grid(.~season) +
  labs(y="Individuals", x="Seasonal count of influenza cases")

data.1011 <- data %>%
  filter(season=="2010-2011")
hh.1011 <- data.1011 %>%
  group_by(master_house_id) %>%
  summarise(nmem = length(master_id), hh.flu.total = sum(flu.count, na.rm = T))
  
data.1112 <- data %>%
  filter(season=="2011-2012")
hh.1112 <- data.1112 %>%
  group_by(master_house_id) %>%
  summarise(nmem = length(master_id), hh.flu.total = sum(flu.count, na.rm = T))

data.1213 <- data %>%
  filter(season=="2012-2013")
hh.1213 <- data.1213 %>%
  group_by(master_house_id) %>%
  summarise(nmem = length(master_id), hh.flu.total = sum(flu.count, na.rm = T))

data.1314 <- data %>%
  filter(season=="2013-2014")
hh.1314 <- data.1314 %>%
  group_by(master_house_id) %>%
  summarise(nmem = length(master_id), hh.flu.total = sum(flu.count, na.rm = T))

data.1415 <- data %>%
  filter(season=="2014-2015")
hh.1415 <- data.1415 %>%
  group_by(master_house_id) %>%
  summarise(nmem = length(master_id), hh.flu.total = sum(flu.count, na.rm = T))

data.1516 <- data %>%
  filter(season=="2015-2016")
hh.1516 <- data.1516 %>%
  group_by(master_house_id) %>%
  summarise(nmem = length(master_id), hh.flu.total = sum(flu.count, na.rm = T))

data.1617 <- data %>%
  filter(season=="2016-2017")
hh.1617 <- data.1617 %>%
  group_by(master_house_id) %>%
  summarise(nmem = length(master_id), hh.flu.total = sum(flu.count, na.rm = T))
table(hh.1617$nmem)

data.1718 <- data %>%
  filter(season=="2017-2018")
hh.1718 <- data.1718 %>%
  group_by(master_house_id) %>%
  summarise(nmem = length(master_id), hh.flu.total = sum(flu.count, na.rm = T))
table(hh.1718$nmem)
```

_Individual demographics_
```{r Table1}
# Baseline demographics
ind.data <- data %>%
  group_by(master_id) %>%
  filter(row_number()==1) %>%
  select(master_id, master_house_id, season, agecat, sex, race, highrisk, covprop.cat)

table(ind.data$covprop.cat)

table(ind.data$agecat)
table(ind.data$sex)
table(ind.data$race)
table(ind.data$highrisk)
table(ind.data$sex, ind.data$agecat)
table(ind.data$race, ind.data$agecat)
table(ind.data$highrisk, ind.data$agecat)

# Person Time
table(data$covprop.cat)

table(data$agecat, data$covprop.cat)
table(data$sex, data$covprop.cat)
table(data$race, data$covprop.cat)
table(data$highrisk, data$covprop.cat)

table(data$sex, data$agecat)
table(data$race, data$agecat)
table(data$highrisk, data$agecat)
```

_Household Vaccine Coverage_
Examine total vaccine coverage by season.
```{r Fig1}

# Person time for each vaccine category
table(data$vax, data$covprop.cat)

hh.data <- data %>%
  distinct(master_house_id, season, covprop, covprop.cat, HHsize, child.covprop, prek.covprop, k12.covprop) %>%
  select(master_house_id, season, covprop, covprop.cat, HHsize, child.covprop, prek.covprop, k12.covprop)

hh.data.only <- hh.data %>%
  group_by(master_house_id) %>%
  summarise(fol.up = length(season)) %>%
  distinct(master_house_id, fol.up)

hh.data$HHsize[hh.data$HHsize==">= 6"] <- "6+"
hh.data$HHsize <- as.factor(hh.data$HHsize)
class(hh.data$HHsize)
hh.data$HHsize <- factor(hh.data$HHsize, levels = c("6+","5","4","3"))

hh.cov.seas <- table(hh.data$covprop.cat, hh.data$season)

setwd("C:/Users/rmalosh/Box Sync/Indirect Effects R03/Aim 1/")

ggsave("R Output/VaxCovSeasSize.png", width = 9, height = 6, units="in")
ggplot(hh.data, aes(covprop, fill=HHsize)) +
  geom_histogram(binwidth = .25) +
  scale_fill_viridis_d() +
  theme_bw() +
  xlab("Proportion of household vaccinated") +
  ylab("Number of households") +
  facet_grid(.~season)

childcov.hist <- ggplot(hh.data, aes(child.covprop, fill=HHsize)) +
  geom_histogram(binwidth = .25) +
  scale_fill_viridis_d() +
  theme_bw() +
  xlab("Proportion of household vaccinated") +
  ylab("Number of households") +
  facet_grid(.~season)

prekcov.hist <- ggplot(hh.data, aes(prek.covprop, fill=HHsize)) +
  geom_histogram(binwidth = .25) +
  scale_fill_viridis_d() +
  theme_bw() +
  xlab("Proportion of household vaccinated") +
  ylab("Number of households") +
  facet_grid(.~season)

k12cov.hist <- ggplot(hh.data, aes(k12.covprop, fill=HHsize)) +
  geom_histogram(binwidth = .25) +
  scale_fill_viridis_d() +
  theme_bw() +
  xlab("Proportion of household vaccinated") +
  ylab("Number of households") +
  facet_grid(.~season)

library(cowplot)
setwd("C:/Users/rmalosh/Box Sync/Indirect Effects R03/Aim 1/")
ggsave("R Output/OthCovSeasSize.png", width = 9, height = 9, units="in")
plot_grid(childcov.hist, prekcov.hist, k12cov.hist, labels = c('A', 'B', 'C'), ncol=1, label_size = 12)
```

_Incidence of influenza_
Estimate the crude incidence rate of influenza by household vaccine coverage each season overall and by type/subtype

```{r inc}
library(epitools)

table(data$flu.count, data$covprop.cat)
table(data$flu.count[data$vax==0], data$covprop.cat[data$vax==0])

ir.unvax <- pois.exact(164, pt=1636)
ir.low <- pois.exact(114, pt=1430)
ir.mod <- pois.exact(100, pt=1495)
ir.full <- pois.exact(379, pt=4804)
ir.all <- bind_rows(ir.unvax, ir.low, ir.mod, ir.full)
ir.all$covprop.cat <- as.factor(c("0","1","2","3"))
ir.all

ir.low.unvax <- pois.exact(88, pt=958)
ir.low.unvax
ir.mod.unvax <- pois.exact(25, pt=386)
ir.mod.unvax
# Incidence rate by coverage 2010-2011
table(data.1011$flu.count, data.1011$covprop.cat)

ir.unvax.1011 <- pois.exact(35, pt=311)
ir.low.1011 <- pois.exact(21, pt=203)
ir.mod.1011 <- pois.exact(22, pt=261)
ir.full.1011 <- pois.exact(52, pt=666)
ir.all.1011 <- bind_rows(ir.unvax.1011, ir.low.1011, ir.mod.1011, ir.full.1011)
ir.all.1011$covprop.cat <- as.factor(c("0","1","2","3"))
ir.all.1011$season <- "2010-2011"
ir.all.1011

# Incidence rate by coverage 2011-2012
table(data.1112$flu.count, data.1112$covprop.cat)

ir.unvax.1112 <- pois.exact(2, pt=196)
ir.low.1112 <- pois.exact(4, pt=163)
ir.mod.1112 <- pois.exact(7, pt=149)
ir.full.1112 <- pois.exact(17, pt=435)
ir.all.1112 <- bind_rows(ir.unvax.1112, ir.low.1112, ir.mod.1112, ir.full.1112)
ir.all.1112$covprop.cat <- as.factor(c("0","1","2","3"))
ir.all.1112$season <- "2011-2012"
ir.all.1112

# Incidence rate by coverage 2012-2013
table(data.1213$flu.count, data.1213$covprop.cat)

ir.unvax.1213 <- pois.exact(32, pt=283)
ir.low.1213 <- pois.exact(14, pt=233)
ir.mod.1213 <- pois.exact(12, pt=201)
ir.full.1213 <- pois.exact(59, pt=719)
ir.all.1213 <- bind_rows(ir.unvax.1213, ir.low.1213, ir.mod.1213, ir.full.1213)
ir.all.1213$covprop.cat <- as.factor(c("0","1","2","3"))
ir.all.1213$season <- "2012-2013"
ir.all.1213

# Incidence rate by coverage 2013-2014
table(data.1314$flu.count, data.1314$covprop.cat)

ir.unvax.1314 <- pois.exact(27, pt=213)
ir.low.1314 <- pois.exact(9, pt=128)
ir.mod.1314 <- pois.exact(3, pt=127)
ir.full.1314 <- pois.exact(13, pt=581)
ir.all.1314 <- bind_rows(ir.unvax.1314, ir.low.1314, ir.mod.1314, ir.full.1314)
ir.all.1314$covprop.cat <- as.factor(c("0","1","2","3"))
ir.all.1314$season <- "2013-2014"
ir.all.1314

# Incidence rate by coverage 2014-2015
table(data.1415$flu.count, data.1415$covprop.cat)

ir.unvax.1415 <- pois.exact(32, pt=215)
ir.low.1415 <- pois.exact(42, pt=243)
ir.mod.1415 <- pois.exact(18, pt=228)
ir.full.1415 <- pois.exact(118, pt=745)
ir.all.1415 <- bind_rows(ir.unvax.1415, ir.low.1415, ir.mod.1415, ir.full.1415)
ir.all.1415$covprop.cat <- as.factor(c("0","1","2","3"))
ir.all.1415$season <- "2014-2015"
ir.all.1415

# Incidence rate by coverage 2015-2016
table(data.1516$flu.count, data.1516$covprop.cat)

ir.unvax.1516 <- pois.exact(8, pt=149)
ir.low.1516 <- pois.exact(1, pt=179)
ir.mod.1516 <- pois.exact(6, pt=145)
ir.full.1516 <- pois.exact(24, pt=523)
ir.all.1516 <- bind_rows(ir.unvax.1516, ir.low.1516, ir.mod.1516, ir.full.1516)
ir.all.1516$covprop.cat <- as.factor(c("0","1","2","3"))
ir.all.1516$season <- "2015-2016"
ir.all.1516

# Incidence rate by coverage 2016-2017
table(data.1617$flu.count, data.1617$covprop.cat)

ir.unvax.1617 <- pois.exact(14, pt=127)
ir.low.1617 <- pois.exact(16, pt=157)
ir.mod.1617 <- pois.exact(19, pt=180)
ir.full.1617 <- pois.exact(30, pt=426)
ir.all.1617 <- bind_rows(ir.unvax.1617, ir.low.1617, ir.mod.1617, ir.full.1617)
ir.all.1617$covprop.cat <- as.factor(c("0","1","2","3"))
ir.all.1617$season <- "2016-2017"
ir.all.1617

# Incidence rate by coverage 2017-2018
table(data.1718$flu.count, data.1718$covprop.cat)

ir.unvax.1718 <- pois.exact(14, pt=142)
ir.low.1718 <- pois.exact(7, pt=134)
ir.mod.1718 <- pois.exact(13, pt=204)
ir.full.1718 <- pois.exact(66, pt=709)
ir.all.1718 <- bind_rows(ir.unvax.1718, ir.low.1718, ir.mod.1718, ir.full.1718)
ir.all.1718$covprop.cat <- as.factor(c("0","1","2","3"))
ir.all.1718$season <- "2017-2018"
ir.all.1718

ir.all.1018 <- bind_rows(ir.all.1011, ir.all.1112, ir.all.1213, ir.all.1314, ir.all.1415, ir.all.1516, ir.all.1617, ir.all.1718)

setwd("C:/Users/rmalosh/Box Sync/Indirect Effects R03/Aim 1/")
ggsave("R Output/IncRateVaxCov.png", width = 9, height = 6, units="in")
ggplot(ir.all.1018, aes(as.factor(covprop.cat), rate, group=season, colour=season)) +
  geom_point(size=3) +
  geom_path() +
  geom_pointrange(aes(ymin=lower, ymax=upper), alpha=.5) +
  scale_x_discrete(labels=c("0", "0.01-0.5", "0.5-0.99", "1")) +
  facet_grid(.~season) +
  theme_bw() +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust=1)) +
  xlab("Proportion of Household Vaccinated") +
  ylab("Incidence Rate (person-season)")


x <- c(164,88,25)
y <- c(1636,958,386)
ir.ind <- matrix(c(x,y), ncol=2)
rateratio.wald(ir.ind, conf.level = .95)

```
_Indirect Effects_
Estimate the indirect effect of vaccination by comparing the incidence rate of influenza among **unvaccinated** members of unvaccinated households to **unvaccinated** members of low and high coverage households adjusting for age category, sex, and high risk condition

```{r model}
library(lme4)
library(boot)
library(glmmTMB)

table(data$vax)

mod0 <- glm(flu.count ~ as.factor(covprop.cat), data=subset(data, vax==0), family=poisson)
summary(mod0)
1-exp(mod0$coefficients)
1-exp(confint(mod0))

# Unadjusted mixed effects with random intercept for individual, household, and season
mod1 <- glmer(flu.count ~ as.factor(covprop.cat) + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0), family=poisson, control=glmerControl(optimizer="Nelder_Mead"))

summary(mod1)
1-exp(fixef(mod1))

# Adjusted for age group, sex, random effects for individual, household, and season
mod2a <- glmer(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0), family=poisson, control=glmerControl(optimizer="bobyqa"))

summary(mod2a)
1-exp(fixef(mod2a))

mod2b <- glmer(flu.count ~ as.factor(covprop.cat) + sex + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0), family=poisson, control=glmerControl(optimizer="bobyqa"))

summary(mod2b)
1-exp(fixef(mod2b))

mod2 <- glmer(flu.count ~ as.factor(covprop.cat)  + as.factor(agecat) + sex + highrisk + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0), family=poisson, control=glmerControl(optimizer="bobyqa"))

summary(mod2)

cis.mod2 <- confint.merMod(mod2, method = "Wald")
cis.mod2
mod2.tbl <- tibble(est=100*(1-exp(c(fixef(mod2)[2], fixef(mod2)[3]))),
                   low.ci=100*(1-exp(c(cis.mod2[5,2], cis.mod2[6,2]))),
                   hi.ci=100*(1-exp(c(cis.mod2[5,1], cis.mod2[6,1])))
                   )
mod2.tbl

# Model season as a random effect
mod3 <- glmer(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + highrisk + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0), family="poisson", glmerControl(optimizer = "Nelder_Mead"))

mod3.nb <- glmmTMB(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + highrisk + (1|master_id) + (1|master_house_id), data=subset(data, vax==0), family="nbinom2")

# These models do not converge, try ZIP

# Zero-inflated poisson
mod4 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + highrisk + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0), ziformula = ~1, family = "poisson")

summary(mod4)
cis.mod4 <- confint(mod4, method="Wald")
cis.mod4

mod4.tbl <- tibble(est=100*(1-exp(c(cis.mod4[2,3], cis.mod4[3,3]))),
                   low.ci=100*(1-exp(c(cis.mod4[2,2], cis.mod4[3,2]))),
                   hi.ci=100*(1-exp(c(cis.mod4[2,1], cis.mod4[3,1])))
                   )
mod4.tbl
```
Comparing the AIC for the standard poisson and zero-inflated poisson models, the AIC is lower for the standard poisson. Report the results of this model


```{r season}
#2010-2011
mod.1011 <- glmer(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + (1|master_house_id), data=subset(data.1011, vax==0), family=poisson, control=glmerControl(optimizer="bobyqa"))
summary(mod.1011)
exp(fixef(mod.1011))

ci.mod1011 <- confint.merMod(mod.1011, method = "profile")
ci.mod1011[3,1]

mod1011.tbl <- tibble(est=1-exp(fixef(mod.1011)[2:3]),
                   low=1-exp(c(ci.mod1011[3,2],ci.mod1011[4,2])),
                   hi=1-exp(c(ci.mod1011[3,1],ci.mod1011[4,1])))
mod1011.tbl

#2011-2012
mod.1112 <- glmer(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + (1|master_house_id), data=subset(data.1112, vax==0), family=poisson, control=glmerControl(optimizer="bobyqa"))
summary(mod.1112)
exp(fixef(mod.1112))

ci.mod1112 <- confint.merMod(mod.1112, method = "profile")
ci.mod1112[3,1]

mod1112.tbl <- tibble(est=1-exp(fixef(mod.1112)[2:3]),
                   low=1-exp(c(ci.mod1112[3,2],ci.mod1112[4,2])),
                   hi=1-exp(c(ci.mod1112[3,1],ci.mod1112[4,1])))
mod1112.tbl

#2012-2013
mod.1213 <- glmer(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + (1|master_house_id), data=subset(data.1213, vax==0), family=poisson, control=glmerControl(optimizer="bobyqa"))
summary(mod.1213)
exp(fixef(mod.1213))

ci.mod1213 <- confint.merMod(mod.1213, method = "profile")
ci.mod1213[3,1]

mod1213.tbl <- tibble(est=1-exp(fixef(mod.1213)[2:3]),
                   low=1-exp(c(ci.mod1213[3,2],ci.mod1213[4,2])),
                   hi=1-exp(c(ci.mod1213[3,1],ci.mod1213[4,1])))
mod1213.tbl

#2013-2014
mod.1314 <- glmer(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + (1|master_house_id), data=subset(data.1314, vax==0), family=poisson, control=glmerControl(optimizer="bobyqa"))
summary(mod.1314)
exp(fixef(mod.1314))

ci.mod1314 <- confint.merMod(mod.1314, method = "profile")
ci.mod1314[3,1]

mod1314.tbl <- tibble(est=1-exp(fixef(mod.1314)[2:3]),
                   low=1-exp(c(ci.mod1314[3,2],ci.mod1314[4,2])),
                   hi=1-exp(c(ci.mod1314[3,1],ci.mod1314[4,1])))
mod1314.tbl

#2014-2015
mod.1415 <- glmer(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + (1|master_house_id), data=subset(data.1415, vax==0), family=poisson, control=glmerControl(optimizer="bobyqa"))
summary(mod.1415)
exp(fixef(mod.1415))

ci.mod1415 <- confint.merMod(mod.1415, method = "profile")
ci.mod1415[3,1]

mod1415.tbl <- tibble(est=1-exp(fixef(mod.1415)[2:3]),
                   low=1-exp(c(ci.mod1415[3,2],ci.mod1415[4,2])),
                   hi=1-exp(c(ci.mod1415[3,1],ci.mod1415[4,1])))
mod1415.tbl

#2015-2016
mod.1516 <- glmer(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + (1|master_house_id), data=subset(data.1516, vax==0), family=poisson, control=glmerControl(optimizer="bobyqa"))
summary(mod.1516)
exp(fixef(mod.1516))

ci.mod1516 <- confint.merMod(mod.1516, method = "profile")
ci.mod1516[3,1]

mod1516.tbl <- tibble(est=1-exp(fixef(mod.1516)[2:3]),
                   low=1-exp(c(ci.mod1516[3,2],ci.mod1516[4,2])),
                   hi=1-exp(c(ci.mod1516[3,1],ci.mod1516[4,1])))
mod1516.tbl

#2016-2017
mod.1617 <- glmer(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + (1|master_house_id), data=subset(data.1617, vax==0), family=poisson, control=glmerControl(optimizer="bobyqa"))
summary(mod.1617)
exp(fixef(mod.1617))

ci.mod1617 <- confint.merMod(mod.1617, method = "profile")
ci.mod1617[3,1]

mod1617.tbl <- tibble(est=1-exp(fixef(mod.1617)[2:3]),
                   low=1-exp(c(ci.mod1617[3,2],ci.mod1617[4,2])),
                   hi=1-exp(c(ci.mod1617[3,1],ci.mod1617[4,1])))
mod1617.tbl


#2017-2018
mod.1718 <- glmer(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + (1|master_house_id), data=subset(data.1718, vax==0), family=poisson, control=glmerControl(optimizer="bobyqa"))
summary(mod.1718)
exp(fixef(mod.1718))

ci.mod1718 <- confint.merMod(mod.1718, method = "Wald")
ci.mod1718[3,1]

mod1718.tbl <- tibble(est=1-exp(fixef(mod.1718)[2:3]),
                   low=1-exp(c(ci.mod1718[3,2],ci.mod1718[4,2])),
                   hi=1-exp(c(ci.mod1718[3,1],ci.mod1718[4,1])))
mod1718.tbl

mod1018.tbl <- bind_rows(mod1011.tbl, mod1112.tbl, mod1213.tbl, mod1314.tbl, mod1415.tbl, mod1516.tbl, mod1617.tbl, mod1718.tbl)

mod1018.tbl

```

```{r indeff.type}
# H3N2
mod.h3 <- glmmTMB(h3.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex  + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0), ziformula = ~1, family = "poisson")

summary(mod.h3)
cis.modh3 <- confint(mod.h3)

modh3.tbl <- tibble(est=100*(1-exp(c(cis.modh3[2,3], cis.modh3[3,3]))),
                   low.ci=100*(1-exp(c(cis.modh3[2,2], cis.modh3[3,2]))),
                   hi.ci=100*(1-exp(c(cis.modh3[2,1], cis.modh3[3,1])))
                   )
modh3.tbl

# H1N1
mod.h1 <- glmmTMB(h1.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex  + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0), ziformula = ~1, family = "poisson")

summary(mod.h1)
cis.modh1 <- confint(mod.h1)

modh1.tbl <- tibble(est=100*(1-exp(c(cis.modh1[2,3], cis.modh1[3,3]))),
                   low.ci=100*(1-exp(c(cis.modh1[2,2], cis.modh1[3,2]))),
                   hi.ci=100*(1-exp(c(cis.modh1[2,1], cis.modh1[3,1])))
                   )
modh1.tbl

mod.b <- glmmTMB(b.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex  + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0), ziformula = ~1, family = "poisson")

# Flu B
summary(mod.b)
cis.modb <- confint(mod.b)

modb.tbl <- tibble(est=100*(1-exp(c(cis.modb[2,3], cis.modb[3,3]))),
                   low.ci=100*(1-exp(c(cis.modb[2,2], cis.modb[3,2]))),
                   hi.ci=100*(1-exp(c(cis.modb[2,1], cis.modb[3,1])))
                   )
modb.tbl

```

```{r age}
# Age-stratified

mod5 <- glmer(flu.count ~ as.factor(covprop.cat) + sex + highrisk + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0 & agecat=="<5"), family = "poisson")

cis.mod5 <- confint(mod5, method="Wald")
cis.mod5

mod5.tbl <- tibble(est=100*(1-exp(c(fixef(mod5)[2:3]))),
                   low.ci=100*(1-exp(c(cis.mod5[5,2], cis.mod5[6,2]))),
                   hi.ci=100*(1-exp(c(cis.mod5[5,1], cis.mod5[6,1])))
                   )
mod5.tbl

mod6 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + sex  + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0 & agecat=="5-17"), ziformula = ~1, family = "poisson")

cis.mod6 <- confint(mod6)
cis.mod6

mod6.tbl <- tibble(est=100*(1-exp(c(cis.mod6[2,3], cis.mod6[3,3]))),
                   low.ci=100*(1-exp(c(cis.mod6[2,2], cis.mod6[3,2]))),
                   hi.ci=100*(1-exp(c(cis.mod6[2,1], cis.mod6[3,1])))
                   )
mod6.tbl

mod7 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + sex  + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0 & agecat=="18+"), ziformula = ~1, family = "poisson")

cis.mod7 <- confint(mod7)
cis.mod7

mod7.tbl <- tibble(est=100*(1-exp(c(cis.mod7[2,3], cis.mod7[3,3]))),
                   low.ci=100*(1-exp(c(cis.mod7[2,2], cis.mod7[3,2]))),
                   hi.ci=100*(1-exp(c(cis.mod7[2,1], cis.mod7[3,1])))
                   )
mod7.tbl
```

_Use proportion of children vaccinated as predictor_

```{r child}
mod8 <- glmmTMB(flu.count ~ as.factor(child.covprop.cat) + as.factor(agecat) + sex + highrisk + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0), ziformula = ~1, family = "poisson")

summary(mod8)
cis.mod8 <- confint(mod8, method="Wald")

mod8.tbl <- tibble(est=100*(1-exp(c(cis.mod8[2,3], cis.mod8[3,3]))),
                   low.ci=100*(1-exp(c(cis.mod8[2,2], cis.mod8[3,2]))),
                   hi.ci=100*(1-exp(c(cis.mod8[2,1], cis.mod8[3,1])))
                   )
mod8.tbl

```
```{r prek}
mod9 <- glmmTMB(flu.count ~ as.factor(prek.covprop.cat) + as.factor(agecat) + sex + highrisk + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0 & HHprek>=1), ziformula = ~1, family = "poisson")

summary(mod9)
cis.mod9 <- confint(mod9, method="Wald")

mod9.tbl <- tibble(est=100*(1-exp(c(cis.mod9[2,3], cis.mod9[3,3]))),
                   low.ci=100*(1-exp(c(cis.mod9[2,2], cis.mod9[3,2]))),
                   hi.ci=100*(1-exp(c(cis.mod9[2,1], cis.mod9[3,1])))
                   )
mod9.tbl

```
```{r k12}
mod10 <- glmmTMB(flu.count ~ as.factor(k12.covprop.cat) + as.factor(agecat) + sex + highrisk + (1|master_id) + (1|master_house_id) + (1|season), data=subset(data, vax==0 & HHk12>=1), ziformula = ~1, family = "poisson")

summary(mod10)
cis.mod10 <- confint(mod10, method="Wald")

mod10.tbl <- tibble(est=100*(1-exp(c(cis.mod10[2,3], cis.mod10[3,3]))),
                   low.ci=100*(1-exp(c(cis.mod10[2,2], cis.mod10[3,2]))),
                   hi.ci=100*(1-exp(c(cis.mod10[2,1], cis.mod10[3,1])))
                   )
mod10.tbl

```
_Total Effects_
Estimate the total effect of vaccination by comparing the incidence rate of influenza among **unvaccinated members** of low and high vaccine coverage households to **vaccinated** members of low and high vaccine coverage households adjusting for age category, sex, and high risk condition
```{r total}
table(data$flu.count[data$vax==1], data$covprop.cat[data$vax==1])
table(data$flu.count[data$vax==0], data$covprop.cat[data$vax==0])

ir.vax <- pois.exact(379, pt=4804)
ir.vax

ir.mod.vax <- pois.exact(75, pt=1109)
ir.mod.vax

ir.low.vax <- pois.exact(26, pt=472)
ir.low.vax

cases <- c(379,75,26, 164) 
pt <- c(4804, 1109, 472, 1636)
ir.tot <- matrix(c(cases, pt), ncol=2)

rateratio(ir.tot, method="wald", rev="r")

```

```{r tot.mod}
tot.effect <- data %>%
  mutate(tot.effect = ifelse(vax==0 & covprop==0, 1,
                             ifelse(vax==1 & covprop>0, 1, 0)))
table(tot.effect$tot.effect)

# Simple poisson to see if we can recover estimates from crude incidence rate ratio
mod11 <- glm(flu.count ~ as.factor(covprop.cat), family="poisson", data=subset(tot.effect, tot.effect==1))
summary(mod11)
1-exp(coef(mod11))

# Unadjusted model with random effects
mod12 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + (1|master_id) + (1|master_house_id) + (1|season), family="poisson", ziformula = ~1, data=subset(tot.effect, tot.effect==1)) 
summary(mod12)

cis.mod12 <- confint(mod12, method="Wald")
cis.mod12

mod12.tbl <- tibble(est=100*(1-exp(c(cis.mod12[2,3], cis.mod12[3,3], cis.mod12[4,3]))),
                   low.ci=100*(1-exp(c(cis.mod12[2,2], cis.mod12[3,2], cis.mod12[4,2]))),
                   hi.ci=100*(1-exp(c(cis.mod12[2,1], cis.mod12[3,1], cis.mod12[4,1])))
                   )
mod12.tbl


# Adjusted ZIP model with random effects
mod13 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + highrisk + (1|master_id) + (1|master_house_id) + (1|season), family="poisson", ziformula = ~1, data=subset(tot.effect, tot.effect==1)) 
summary(mod13)

cis.mod13 <- confint(mod13, method="Wald")
cis.mod13

mod13.tbl <- tibble(est=100*(1-exp(c(cis.mod13[2,3], cis.mod13[3,3], cis.mod13[4,3]))),
                   low.ci=100*(1-exp(c(cis.mod13[2,2], cis.mod13[3,2], cis.mod13[4,2]))),
                   hi.ci=100*(1-exp(c(cis.mod13[2,1], cis.mod13[3,1], cis.mod13[4,1])))
                   )
mod13.tbl
```

```{r tot.seas}
mod.tot1011 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + highrisk +  (1|master_house_id), family="poisson", ziformula = ~1, data=subset(tot.effect, tot.effect==1 & season=="2010-2011")) 
summary(mod.tot1011)

cis.mod.tot1011 <- confint(mod.tot1011, method="Wald")
modtot1011.tbl <- tibble(est=100*(1-exp(c(cis.mod.tot1011[2,3], cis.mod.tot1011[3,3], cis.mod.tot1011[4,3]))),
                   low.ci=100*(1-exp(c(cis.mod.tot1011[2,2], cis.mod.tot1011[3,2], cis.mod.tot1011[4,2]))),
                   hi.ci=100*(1-exp(c(cis.mod.tot1011[2,1], cis.mod.tot1011[3,1], cis.mod.tot1011[4,1])))
                   )
modtot1011.tbl

# 2011-2012
mod.tot1112 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + (1|master_house_id), family="nbinom2", ziformula = ~1, data=subset(tot.effect, tot.effect==1 & season=="2011-2012")) 
summary(mod.tot1112)

cis.mod.tot1112 <- confint(mod.tot1112, method="Wald")
modtot1112.tbl <- tibble(est=100*(1-exp(c(cis.mod.tot1112[2,3], cis.mod.tot1112[3,3], cis.mod.tot1112[4,3]))),
                   low.ci=100*(1-exp(c(cis.mod.tot1112[2,2], cis.mod.tot1112[3,2], cis.mod.tot1112[4,2]))),
                   hi.ci=100*(1-exp(c(cis.mod.tot1112[2,1], cis.mod.tot1112[3,1], cis.mod.tot1112[4,1])))
                   )
modtot1112.tbl

# 2012-2013
mod.tot1213 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + highrisk +  (1|master_house_id), family="nbinom2", ziformula = ~1, data=subset(tot.effect, tot.effect==1 & season=="2012-2013")) 
summary(mod.tot1213) 

cis.mod.tot1213 <- confint(mod.tot1213, method="Wald")
modtot1213.tbl <- tibble(est=100*(1-exp(c(cis.mod.tot1213[2,3], cis.mod.tot1213[3,3], cis.mod.tot1213[4,3]))),
                   low.ci=100*(1-exp(c(cis.mod.tot1213[2,2], cis.mod.tot1213[3,2], cis.mod.tot1213[4,2]))),
                   hi.ci=100*(1-exp(c(cis.mod.tot1213[2,1], cis.mod.tot1213[3,1], cis.mod.tot1213[4,1])))
                   )
modtot1213.tbl

#2013-2014
mod.tot1314 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + highrisk +  (1|master_house_id), family="nbinom2", ziformula = ~1, data=subset(tot.effect, tot.effect==1 & season=="2013-2014")) 
summary(mod.tot1314) 

cis.mod.tot1314 <- confint(mod.tot1314, method="Wald")
modtot1314.tbl <- tibble(est=100*(1-exp(c(cis.mod.tot1314[2,3], cis.mod.tot1314[3,3], cis.mod.tot1314[4,3]))),
                   low.ci=100*(1-exp(c(cis.mod.tot1314[2,2], cis.mod.tot1314[3,2], cis.mod.tot1314[4,2]))),
                   hi.ci=100*(1-exp(c(cis.mod.tot1314[2,1], cis.mod.tot1314[3,1], cis.mod.tot1314[4,1])))
                   )
modtot1314.tbl

#2014-2015
mod.tot1415 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + highrisk +  (1|master_house_id), family="nbinom2", ziformula = ~1, data=subset(tot.effect, tot.effect==1 & season=="2014-2015")) 
summary(mod.tot1415) 

cis.mod.tot1415 <- confint(mod.tot1415, method="Wald")
modtot1415.tbl <- tibble(est=100*(1-exp(c(cis.mod.tot1415[2,3], cis.mod.tot1415[3,3], cis.mod.tot1415[4,3]))),
                   low.ci=100*(1-exp(c(cis.mod.tot1415[2,2], cis.mod.tot1415[3,2], cis.mod.tot1415[4,2]))),
                   hi.ci=100*(1-exp(c(cis.mod.tot1415[2,1], cis.mod.tot1415[3,1], cis.mod.tot1415[4,1])))
                   )
modtot1415.tbl

#2015-2016
mod.tot1516 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + highrisk +  (1|master_house_id), family="nbinom2", ziformula = ~1, data=subset(tot.effect, tot.effect==1 & season=="2015-2016")) 
summary(mod.tot1516) 

cis.mod.tot1516 <- confint(mod.tot1516, method="Wald")
cis.mod.tot1516
modtot1516.tbl <- tibble(est=100*(1-exp(c(cis.mod.tot1516[2,3], cis.mod.tot1516[3,3], cis.mod.tot1516[4,3]))),
                   low.ci=100*(1-exp(c(cis.mod.tot1516[2,2], cis.mod.tot1516[3,2], cis.mod.tot1516[4,2]))),
                   hi.ci=100*(1-exp(c(cis.mod.tot1516[2,1], cis.mod.tot1516[3,1], cis.mod.tot1516[4,1])))
                   )
modtot1516.tbl

#2016-2017
mod.tot1617 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + highrisk +  (1|master_house_id), family="nbinom2", ziformula = ~1, data=subset(tot.effect, tot.effect==1 & season=="2016-2017")) 
summary(mod.tot1617) 

cis.mod.tot1617 <- confint(mod.tot1617, method="Wald")
modtot1617.tbl <- tibble(est=100*(1-exp(c(cis.mod.tot1617[2,3], cis.mod.tot1617[3,3], cis.mod.tot1617[4,3]))),
                   low.ci=100*(1-exp(c(cis.mod.tot1617[2,2], cis.mod.tot1617[3,2], cis.mod.tot1617[4,2]))),
                   hi.ci=100*(1-exp(c(cis.mod.tot1617[2,1], cis.mod.tot1617[3,1], cis.mod.tot1617[4,1])))
                   )
modtot1617.tbl

#2017-2018
mod.tot1718 <- glmmTMB(flu.count ~ as.factor(covprop.cat) + as.factor(agecat) + sex + highrisk +  (1|master_house_id), family="poisson", ziformula = ~1, data=subset(tot.effect, tot.effect==1 & season=="2017-2018")) 
summary(mod.tot1718) 

cis.mod.tot1718 <- confint(mod.tot1718, method="Wald")
modtot1718.tbl <- tibble(est=100*(1-exp(c(cis.mod.tot1718[2,3], cis.mod.tot1718[3,3], cis.mod.tot1718[4,3]))),
                   low.ci=100*(1-exp(c(cis.mod.tot1718[2,2], cis.mod.tot1718[3,2], cis.mod.tot1718[4,2]))),
                   hi.ci=100*(1-exp(c(cis.mod.tot1718[2,1], cis.mod.tot1718[3,1], cis.mod.tot1718[4,1])))
                   )
modtot1718.tbl

```

```{r ve.seas}
setwd("C:/Users/rmalosh/Box Sync/Indirect Effects R03/Aim 1")
ve.est <- read.csv("Data/VE Estimates 2010-2018.csv")

ve.est$vax.cov <- factor(ve.est$vax.cov, levels = c("Low", "Moderate", "Full"))
ggplot(ve.est, aes(ve.type, ve.est, colour=vax.cov)) +
  geom_point(position = position_dodge(width = 0.5), na.rm=T) +
  geom_pointrange(aes(ymin = ve.lo, ymax = ve.hi), position=position_dodge(width = 0.5), na.rm=T) +
  facet_grid(. ~ study.year) +
  theme_bw() +
  scale_color_grey("Household\nVaccine Coverage", end = .66) +
  coord_cartesian(ylim = c(-100,100)) +
  labs(y="Vaccine Effectiveness") +
  geom_hline(aes(yintercept=0), colour="black", linetype="dashed")
ggsave("R Output/VE by Vax Cov 2010-18.png", width = 15, height = 6, units="in")
```